Estimating associations between childhood exposure to non-persistent endocrine disruptors, corticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2023-11-21 output/paper/_tables.qmd
Started writing results.

```{r pop-desc}
#| label: tbl-pop-desc
#| tbl-cap: Population description

@@

```{r edc-desc}
#| label: tbl-edc-desc
#| tbl-cap: Levels of unprocessed chemicals

@@

```{r met-desc}
#| label: tbl-met-desc
#| tbl-cap: Levels of unprocessed corticosteroids

>>>>

```{r pop-desc}
#| label: tbl-pop-desc
#| tbl-cap: Characteristics of the children included in the analyses, by cohort and overall

@@

```{r edc-desc}
#| label: tbl-edc-desc
#| tbl-cap: Levels of unprocessed chemicals, by cohort and overall

@@

```{r met-desc}
#| label: tbl-met-desc
#| tbl-cap: Levels of unprocessed corticosteroids, by cohort and overall

### 2023-11-21 output/paper/manuscript.qmd
Started writing results.

@@

## Outcome data {#sec-res-out-desc}

>>>>

In total, 1,297 children were included in the dataset. Of these, 976 had information also about the corticosteroids. The sample consisted of 55% girls. The median \acr{hitrtse} was 300 ms (\acr{iqr}, 231-368), with lower median values for EDEN, MOBA, and SAB, corresponding to the cohorts with older children. At the time of visit, the median age of the children was 8.06 years. The children were mostly Caucasian (90%) or Pakistani (6.2%). @tbl-pop-desc provides descriptive statistics for the outcome and covariates, by cohort and overall. Codebooks for the used covariates, by research question, are provided in @supptbl-codebook-1, @supptbl-codebook-2, and @supptbl-codebook-3.

@@

Levels of unprocessed non-persistent \acr{edcs} and corticosteroids are presented in @tbl-edc-desc and @tbl-met-desc, respectively.
